---
title: "p8105_hw1_yj2687"
author: "Yijia Jiang"
date: "2022-09-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,echo = FALSE, message = FALSE}
library(tidyverse)
library(ggplot2)
```


## Problem 1

#### Load and describe the dataset.
```{r,message=FALSE}
data("penguins", package = "palmerpenguins")

names_penguins = names(penguins)

skimr::skim(penguins)
  
nrow = nrow(penguins)
ncol = ncol(penguins)

mean_flipper_length = penguins %>%
  drop_na %>% 
  summarise(mean(flipper_length_mm)) %>% 
  round(digits = 2)
```
The size of the dataset is `r nrow` x `r ncol`. <br>
The names of the variables are `r names_penguins`. <br>
The mean flipper length is `r mean_flipper_length`.


#### Make a scatterplot.
```{r,message=FALSE}
scatterplot = penguins %>% 
  drop_na() %>% 
  ggplot() + geom_point(aes(bill_length_mm, flipper_length_mm, color = species))

ggsave("Scatterplot.pdf", plot = scatterplot)
```




## Problem 2

#### Create a data frame.
```{r,message=FALSE}
df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = rep(c("a", "b", "c", "d", "e"), length.out = 10),
  vec_factor = factor(rep(c("high","middle","low"), length.out = 10))
  )
```


#### Calculate the mean of the data frame.
```{r,message=FALSE}
mean(pull(df,vec_numeric))
mean(pull(df,vec_logical))
mean(pull(df,vec_char))
mean(pull(df,vec_factor))
```
The calculation of mean works for numeric and logical vectors, but not for the character and factor vectors.


#### Conversion with as.numeric function.
```{r,message=FALSE,eval=FALSE}
mean(as.numeric((pull(df,vec_logical))))
mean(as.numeric(pull(df,vec_char)))
mean(as.numeric(pull(df,vec_factor)))
```
The logical and factor vectors are successfully converted to numeric vectors, thus their means can be calculated. However, this conversion cannot be applied to character vectors. 


