---
title: "p8105_hw1_yj2687"
author: "Yijia Jiang"
date: "2022-09-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,echo = FALSE, message = FALSE}
library(tidyverse)
```


## Problem 1

#### Load and describe the dataset.
```{r,message=FALSE}
data("penguins", package = "palmerpenguins")

names_penguins = names(penguins)

skimr::skim(penguins)

levels_species = levels(penguins$species)
levels_sex = levels(penguins$sex)
levels_island = levels(penguins$island)

nrow = nrow(penguins)
ncol = ncol(penguins)

mean_flipper_length = penguins %>%
  drop_na %>% 
  summarise(mean(flipper_length_mm)) %>% 
  round(digits = 2)
```
The names of the variables are `r names_penguins`. <br>
The levels of species are `r levels_species`. The levels of sex are `r levels_sex`. The levels of island are `r levels_island`.<br>
The size of the dataset is `r nrow` rows x `r ncol` columns. <br>
The mean flipper length is `r mean_flipper_length`.



#### Make a scatterplot.
```{r,message=FALSE}
scatterplot = penguins %>% 
  drop_na() %>% 
  ggplot() + geom_point(aes(bill_length_mm, flipper_length_mm, color = species))

ggsave("p8105_hw1_scatterplot.pdf", plot = scatterplot)
```




## Problem 2

#### Create a data frame.
```{r,message=FALSE}
df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = rep(c("A", "B", "C", "D", "E"), length.out = 10),
  vec_factor = factor(rep(c("high","middle","low"), length.out = 10))
  )
```


#### Calculate the mean of the data frame.
```{r,message=FALSE}
mean(pull(df,vec_numeric))
mean(pull(df,vec_logical))
mean(pull(df,vec_char))
mean(pull(df,vec_factor))
```
The calculation of mean works for numeric and logical vectors, but not for the character and factor vectors.


#### Conversion with as.numeric function.
```{r,message=FALSE}
mean(as.numeric((pull(df,vec_logical))))
mean(as.numeric(pull(df,vec_char)))
mean(as.numeric(pull(df,vec_factor)))
```
The logical and factor vectors are successfully converted to numeric vectors, however, this conversion cannot be applied to character vectors. This is because converting the logical vector to a numeric vector changed **TRUE to 1** and **FALSE to 0**, converting the factor vector to a numeric vector changed **high level to 1**, **middle level to 2**, and **low level to 3**. Converting the character vector to a numeric vector resulted in the fact that all characters were set to NAs, thus the `mean` function didn't work.


